### 2018-01-01 icde/revision/Response.tex

\geometry{left=2.0cm, right=2.0cm, top=2.5cm, bottom=2.5cm}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\sstab}{\rule{0pt}{8pt}\\[-2.4ex]}

\begin{document}

%Prof. xxx,\\
%Editor-in-Chief,\\
%IEEE International Conference on Data Engineering\\

Dear Meta-Reviewer and Reviewers,

We have revised our submission, \emph{Query Independent Scholarly Article Ranking}, to IEEE International Conference on Data Engineering 2018.

@@

We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.

The paper has been substantially revised according to the referees¡¯ comments. In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.

Below please find our detailed responses to the comments by the referees.

\textbf{Response to the comments of Meta-Reviewer.}

\textbf{[M1]} \emph{The reviewers see some merit in the approach, but they have also raised important concerns regarding the technical depth and novelty of the approach. In particular, the authors use known techniques for an application (scientific article ranking) for which there is abundance of previous work (it even has its own field, called scientometrics, or  bibliometrics).}

We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics. These have never been exploited in existing studies. That is, we are not simply using known techniques for an application.

We also believe that our ensemble based ranking model and the citation statistics revealed in our study have their own interests to the researchers in the field of scientometrics or  bibliometrics.

 We have clarified these in our paper. Thanks for pointing these out!

\textbf{[M2]} \emph{In revising their paper, the authors should try to address all reviewers¡¯ comments and in particular address the required changes for revision by Reviewer 1.}

Yes, we have addressed these. Please refer to our responses below.

@@

%******************* reviewer 1 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 1.}

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

We discuss the necessity and the selection of parameters right after Eq. (7) (left column, page 4). More specifically, these parameters make our model be able to fit to the various ranking scenarios. As shown in the experiment study (Exp-1 and Exp-2), our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters.

Moreover, these parameters are indeed quite flexible to choose within a certain range (Exp-5.3, page 10). Note that (a) the optimal \PairAcc is obtained within a single region, (b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and (c) the optimal parameters on the same set of ground-truth are very similar across different datasets.

@@

%The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

%We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
%
This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search (as we discussed in the first two paragraphs in Section 1).
%
The combination of query dependent ranking and query independent ranking  is well known, e.g., typical search engines such as Google : keyword search (query dependent ranking) is combined with Pagerank (query independent ranking). Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking along the same lines as keyword search.

The extension in {\em other heterogeneous information networks} is currently unclear, since the TWPageRank is designed based on a deep analysis of scholarly articles (left column, page 2). We shall identify the possible applications in other heterogeneous information networks in the future.

@@

\textbf{[R1D1]} \emph{In the time-weighted pagerank algorithm, the impacts are encoded into the edge weight. How about changing the values on nodes?}

%We clarify the reasons of not changing values on nodes at the revised version (Remarks, left column, page 3).
The goal of our TWPageRank is to change node values, \ie importance, through iterations.
%One may wonder why not directly change node values.
An alternative way to do that is to directly change node values. However, it is difficult to handle as importance does not have a clear and closed-form definition. It may also cause problems for convergence.
To our knowledge, there is no related work on changing node weights to achieve this goal, and it is indeed unclear how to handle it. % Finally, we use iterations with impact weights since importance is essentially propagable through edges and it is also fair for all nodes.

@@

\textbf{[R1D2]} \emph{This paper has an important observation that ¡°the impact of an article tends to decay with time after the peak time only.¡± However, I cannot see that from Figure 1. It is better to add some references to support the claim.}

Figure 1 shows the logscale percentage of the number of articles/citations of each year that grows exponentially with time, instead of the number of citations (\ie impacts) of individual articles.
%We have highlighted it in the revised version (Figure 1, page 2).

We have explained our claim better (Time-Weighted PageRank, page 2). The direct decay model only considers the case of {\em MonDec}.
To unify these distinct citation patterns and to make our ranking model succinct, we adopt the claim that the impact of an article tends to decay with time after the peak time.
Moreover, the aging function in [17] exploits a log-normal survival probability that also only decays with time after the citation peak.
%(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).

@@

[17]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we unify the five patterns, and we only use the highest peak time that has been formally defined in Section II-A (para 1, left column, page 3).
Also note that: (a) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (b) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.

@@

[18]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

Yes, we agree that distributed processing is an important way for large scholar graphs.  But this topic is beyond the reach of this study, and we plan to do this in our future work (Conclusions, page 12). Thanks for the suggestion!

### 2018-01-01 icde/revision/Response.tex

%******************* reviewer 3 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 3.}

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, thanks for the nice suggestion! Due to the space limitation, we have added the examples to the full version (https://hurenjun.github.io/SARank-full.pdf).

@@

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10). Thanks for the suggestion!
%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms. seperate exp, between two baselines, author citation graph
%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

\textbf{[R3D1]} \emph{Although the authors have a detailed introduction about the growing data, detailed figures about the data are recommended in the introduction.}

Yes, we  have added the volume statistics (the number of articles published at each year) of the growing data in Figure 1. Thanks!

@@

\textbf{[R3D3]} \emph{It is suggested that the authors should include some references to papers addressing the time delaying problem such as temporal graph, since it is related to the topic.}

Yes. We have discussed the correlation between our work and temporal graphs, and cited necessary references (e.g., P. Holme and J. Saramaki, ¡°Temporal networks,¡± Physics Reports, vol. 519, no. 3, pp. 97 ¨C 125, 2012) in related work (Section VI).

### 2018-01-01 icde/revision/Response.tex

Yes, we have revised our paper as suggested (right column, page 1 \& Table I, page 5). Thanks!
%Thanks for the suggestion!

%******************* reviewer 2 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1\&D1]} 
\emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
\emph{There seem to be two ``contradictory" sides to this paper. From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

Yes, our work comes from a practical need from industries. We thank the reviewer for appreciating this merit of our work.

More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years. In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption. Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics (\eg for the maintenance of the topological order), both of which have never been exploited before.

We have further clarified this both in the contributions and in the related work.

%
%To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
%We have further %clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.

@@

%
%To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
%We have further %clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.

%The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions. Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.

%\marked{In the revised version, we highlight our technical contributions.}

%[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.

@@

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper, and tried our test to improve its presentation.
%Thanks for the suggestion!

@@

\textbf{[R2D2]} \emph{The abstract starts with the sentence ``Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really ``critical".}

We have downgraded the tone and changed it into ``a practical and difficult problem''. Thanks for the suggestion!

@@

\textbf{[R2D3]} \emph{On page 4, you say ``However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle ``on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We agree that this sentence does not make sense, and, hence, we have removed the sentence, and explained more details about the statement (Author Component, left column, page 4). Thanks!

Yes, distributed processing is adopted for Pangrank computation at Google, and we plan to develop a distributed version of our algorithm as well. 
However, even this, memory cost should also be deliberately considered in a centralized case.

One way to compute the prestige of authors is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.

This needs quite a few space, and  the generated author citation graph has 7.12 billion edges on the largest \magdata (its memory cost of storage is 57GB).
This is why we choose to evaluate the prestige of an author with the average prestige of all articles published by the author.

@@

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, thanks for the nice suggestion! Due to the space limitation, we have added the examples to the full version (https://hurenjun.github.io/SARank-full.pdf).

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 10). Thanks for the suggestion!
%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms. seperate exp, between two baselines, author citation graph
%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2018-01-02 icde/revision/Response.tex

Dear Meta-Reviewer and Reviewers,

We have revised our submission, \emph{Query Independent Scholarly Article Ranking}, to IEEE International Conference on Data Engineering 2018.

We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.

The paper has been substantially revised according to the referees' comments. In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our techniques with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.

@@

%******************* reviewer 1 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 1.}

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

We discuss the necessity and the selection of parameters right after Eq. (7) (left column, page 4). More specifically, these parameters make our model be able to fit to the various ranking scenarios. As shown in the experimental study (Exp-1 and Exp-2), our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters.

Moreover, these parameters are indeed quite flexible to choose within a certain range (Exp-5.3, page 10). Note that (1) the optimal \PairAcc is obtained within a single region, (2) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and (3) the optimal parameters on the same set of ground-truth are very similar across different datasets.

@@

%The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

%We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
%
This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search (as we discussed in the first two paragraphs in Section I).
%
The combination of query dependent ranking and query independent ranking  is well known, e.g., typical search engines such as Google: keyword search (query dependent ranking) is combined with PageRank (query independent ranking). Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking along the same lines as keyword search.

@@

We have explained our claim better (Time-Weighted PageRank, page 2). The direct decay model only considers the case of {\em MonDec}.
To unify these distinct citation patterns and to make our ranking model succinct, we adopt the claim that the impact of an article tends to decay with time after the peak time.
Moreover, the aging function in [17] exploits a log-normal survival probability that also only decays with time after the citation peak.
%(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).

[17]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we unify the five patterns, and we only use the highest peak that has been formally defined in Section II-A (para 1, left column, page 3).
Also note that: (1) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (2) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.

@@

Yes, we have revised our paper as suggested (right column, page 1 \& Table I, page 5). Thanks!
%Thanks for the suggestion!

%******************* reviewer 2 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1\&D1]}
\emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
\emph{There seem to be two ``contradictory" sides to this paper. From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. PageRank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

@@

%
%To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
%We have further %clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.

%The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions. Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.

%\marked{In the revised version, we highlight our technical contributions.}

[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.

@@

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper, and tried our best to improve its presentation.
%Thanks for the suggestion!

@@

We have downgraded the tone and changed it into ``a practical and difficult problem''. Thanks for the suggestion!

\textbf{[R2D3]} \emph{On page 4, you say ``However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle ``on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We agree that this sentence does not make sense, and, hence, we have removed the sentence, and explained more details about the statement (Author Component, left column, page 4). Thanks!

Yes, distributed processing is adopted for PangRank computation at Google, and we plan to develop a distributed version of our algorithm as well.
However, even this, memory cost should also be deliberately considered in a centralized case.

@@

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, thanks for the nice suggestion! Due to the space limitation, we have added the examples to the full version (https://hurenjun.github.io/SARank-full.pdf).

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 9). Thanks for the suggestion!
%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms. seperate exp, between two baselines, author citation graph
%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2018-01-02 icde/revision/sec-app.tex

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-graph.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-ranking.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

\stitle{Citation component}.
The first component computes the importance of articles using the citation information.

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest scaled number of citations.

\sstab(1) The prestige of articles is derived by applying TWPageRank on the citation graph $G^c$, and each article $v$ is assigned the corresponding TWPageRank score as its prestige $Prs_c(v)$.

\sstab(2)  The popularity of an article is the sum of all its citation freshness, \ie the closeness to the current year:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

%Alternatively, one may want to define $Pop_c(v) = e^{\sigma \cdot (T_0-T_v)}$, \ie decaying with the publication year $T_v$ of article $v$ directly~\cite{sayyadi09,WalkerXKM07}. We propose to use the publication years $T_u$ of citations, instead of $T_v$, since $T_u$ reflects the ages of articles to some extent, \eg articles are probably cited in the next few years after publication(Fig.~\ref{fig-citation}).

Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores. %, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.
%
%\marked{Different from $Peak_v$ in Eq.~(\ref{eq-infl-weights}), the bias of references has little impacts on the popularity. Moreover, the motivation of popularity is to assign higher ranks to articles of recent attention, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.}
%
Note that the popularity is also normalized such that the sum of  all articles is equal to $1$, similar to the prestige produced by TWPageRank.

\sstab(3) The prestige and popularity are finally combined to produce the importance of articles. Intuitively, an important article is both prestigious and popular. Hence, the {\em citation importance score} $Imp_c(v)$ of an article is defined as a weighted combination of its prestige and popularity:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-imp}
%Imp_c(v) = \sqrt{Prs_c(v) \cdot Pop_c(v)}.
Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
\end{equation}
\end{small}
\noindent where $\lambda \in [0,1]$ is the importance weighting factor.
The rationales behind Eq.~(\ref{eq-imp}) are as follows. (a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.

%Here the prestige and popularity are equally weighted to produce the importance of an article, as we focus on query independent ranking. They may be properly weighted when the query information is available, which is beyond the scope of this work.

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

\stitle{Venue component}.
The second component computes the importance of venues with their associated articles. As the importance of a venue  evolves with time, we treat the venue in each year individually, and its importance is the sum of importance in all individual years.

A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} $w_v(s,t)$ to denote the weight  from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights-v}
w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
\end{equation}
\end{small}
\noindent
Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.

The prestige of a venue in a specific year is computed using the impact weights and the update rule in Eq.~(\ref{eq-twpr}), and the popularity of a venue in a specific year is defined as the average popularity of its articles. The prestige and popularity are combined to derive the importance of a venue in a specific year in the same way as the citation component. Finally, the importance of a venue is treated as the {\em venue importance score} for all articles published in this venue.

\stitle{Author component}.
The author component computes the importance of authors with their published articles.
%
Similar to the venue component, we evaluate the importance of each author, and compute the average importance of the authors of an article as its {\em author importance score}.

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
One way to do this is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.

Hence, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is  defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance along the same way as the citation component.

%, which can be directly obtained from the citation component,
%to evaluate the authority of that author.

\eat{
\stitle{Affiliation ensemble}.
Recall that articles in our data are also associated with affiliation information. Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble. However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues. As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy. Hence, we choose not to use the affiliation ensemble in our model.
}

%\subsection{Ranking with Importance}
%{\label{subsec-eerank}}

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.
%
The final ranking score $R(v)$ is aggregated as follows:

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
which make our model be able to fit to the various ranking scenarios. As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

\stitle{Remarks}. This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}). However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.

>>>>

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-graph.eps}
\vspace{-1ex}
\caption{\small An example of graph generation} \label{fig-example-graph}
\vspace{-3ex}
\end{figure}

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-ranking.eps}
\vspace{-1ex}
\caption{\small An example of ranking model \ensemblerank} \label{fig-example-model}
\vspace{-3ex}
\end{figure}

@@

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-example-graph} illustrates an example of graph generation. We choose four articles of real-life data to show how to generate the citation graph, venue graph and author citation graph while the original academic graph data only has citation information, author-article relationships, article-venue relationships and time information of articles. As shown in Figure~\ref{fig-example-graph}, the articles A, B, C and D represent "Role Discovery in Networks", "On the Use of Side Information for Mining Text Data", "On Text Clustering with Side Information" and "Efficient streaming text clustering", respectively. We next introduce the details of graph generation.

The citation graph is constructed using the citation information such that each node denotes an individual article and the edge $(A,B)$ denotes that article A have cited article B. The venue graph is constructed using the citation information among venues. As shown in Figure~\ref{fig-example-graph}, each node denotes a venue in a specific year such that TKDE-14 and TKDE-15 are two different nodes. Further, each edge denotes that there are citations between the articles published in the two venues. The author citation graph is constructed using the citation information among authors. As shown in Figure~\ref{fig-example-graph}, the article citation between article A and article B will generate 6 different edges in author citation graph, which makes it much more complicated than citation graph. As a result, the citation graph of 4 articles and 4 edges have generated a author citation graph of 6 nodes and 18 edges (the bidirectional arrow denotes two edges) although the article B and article C have shared same authors.

\end{example}

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-example-model} illustrates an example of article ranking model. Consider an article $v$ published by authors $t$ and $u$ in venue $k$.

\end{example}
